### 2021-09-30 README.Rmd
Paper accepted in Geographical Analysis

Paper submitted to [~~PLoS ONE~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/PLOS ONE Decision_ PONE-D-21-16874.pdf) [~~Science of the Total Environment~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/Your Submission STOTEN-D-21-12077.pdf) [~~Landscape and Urban Planning~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/Decision on submission to Landscape and Urban Planning.pdf) Geographical Analysis

>>>>

Paper desk-rejected by [~~PLoS ONE~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/PLOS ONE Decision_ PONE-D-21-16874.pdf) [~~Science of the Total Environment~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/Your Submission STOTEN-D-21-12077.pdf) [~~Landscape and Urban Planning~~](https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed/tree/main/R0-Density-Reanalysis/Decision on submission to Landscape and Urban Planning.pdf)

Forthcoming in Geographical Analysis
